Dynamic Transition Analysis with TIMES

### 2020-11-26 doc/2020-03-paper/Appendix.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

\begin{table}[!ht]
	\caption{Data for initial condition.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{Coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[!ht]

@@

\begin{table}[!ht]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[!ht]
%\begin{minipage}{\textwidth} 
	\caption{Capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Max. Annual} \\
  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
Onshore Wind \cite{irena_renewable_2020} & 25\% \\
Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion Storage & 30\% \\
Natural Gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

\begin{table}[!ht]
	\caption{Miscellaneous model parameters and assumptions.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Currency & MUSD 2015 \\
Activity unit & GWh\\
Discount rate & 5\% \\
Transmission efficiency & 90 \% \\
Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
\hline 
	\end{tabularx}
\label{misc-assump}
\end{table}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.07]{figures/useless}
\caption{Sensitivity analysis results for \gls{PEMFC} and \gls{CCS} coal.}
\label{sa-useless}
\end{figure}

>>>>

\begin{table}[H]
	\caption{Data for initial condition.}
	\vspace{0.1in}
	\begin{tabularx}{1.2\textwidth}{p{0.35\textwidth} p{0.25\textwidth} p{0.2\textwidth} p{0.25\textwidth}}
		\hline
\textbf{Technology} & \textbf{\gls{lcoe}} \cite{lazard_lazards_2016} & \textbf{Emission} & \textbf{Year of total}\\
  & (USD/kWh) & \textbf{Coefficients} \cite{noauthor_electricity_2019} (gCO$_2$-eq. /kWh) & \textbf{retirement} \\
\hline
Coal & 0.06 & 943 & 2030 \\
\gls{lng} & 0.08 & 599 & 2030 \\
Oil & 0.39 & 738 & 2030 \\
Nuclear & 0.11 & 21 & 2069 \\
Hydro & 0.05 & 11 & N.A. \\
Geothermal & 0.12 & 13 & N.A. \\
Wind & 0.11 & 25 & 2040 \\
Solar & 0.15 & 37 & 2040 \\
\hline 
\end{tabularx}
\label{init-eco}
\end{table}

@@

\begin{table}[H]

@@

\begin{table}[H]
	\caption{Capacity limits.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth} }
		\hline
\textbf{Technology} & \textbf{Net Capacity} \textbf{Limit} (GW)\\
\hline
Photovoltaic \cite{isep_53_2018} & 332 \\
Onshore wind \cite{heger_wind_2016,kato_energy_2016} & 180 \\
Offshore wind (fixed) \cite{heger_wind_2016,kato_energy_2016}& 130 \\
Offshore wind (floating) \cite{heger_wind_2016,kato_energy_2016}& 260 \\
Nuclear & 50 (Scenarios 3 \& 4) \\
 & 100 (Scenario 2) \\
\gls{PWS} \cite{pinaud_technical_2013} & 100 (Scenario 5) \\
\hline 
\end{tabularx}
\label{caplim}
\end{table}

\begin{table}[H]
%\begin{minipage}{\textwidth} 
	\caption{Capacity growth rates.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Technology} & \textbf{Max. Annual} \\
  & \textbf{Growth Rate}   \\
\hline
Nuclear (2027 onwards) & +5 reactors \\
Solar and Emerging Solar \cite{irena_renewable_2020} & 40\%  \\
Onshore Wind \cite{irena_renewable_2020} & 25\% \\
Offshore Wind(Fixed) \cite{irena_renewable_2020} & 20\% \\
Offshore Wind(Floating) \cite{irena_renewable_2020} & 20\% \\
Li-ion Storage & 30\% \\
Natural Gas &  50\% \\
\gls{USC} & 50\% \\
All emerging technologies & 40\% (Years 1-5) \\
& 60\% (Years 6-10) \\
 & 40\% (Years 11-15) \\
 & 30\% (Years 16-) \\
\hline 
\end{tabularx}
\label{growrate}
%\end{minipage}
\end{table}

\begin{table}[H]
	\caption{Miscellaneous model parameters and assumptions.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.5\textwidth} p{0.5\textwidth}}
		\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Currency & MUSD 2015 \\
Activity unit & GWh\\
Discount rate & 5\% \\
Transmission efficiency & 90 \% \\
Li-ion discharge time \cite{mongird_energy_2019} & 4h \\
Li-ion E/P ratio \cite{mongird_energy_2019} & 4  \\
Li-ion depth-of-discharge \cite{mongird_energy_2019} & 80\% \\
Li-ion lifetime cycles \cite{mongird_energy_2019} & 3500  \\
\hline 
	\end{tabularx}
\label{misc-assump}
\end{table}

\pagebreak

\subsection{Sensitivity analysis secondary results}

\begin{figure}[H] 
\centering
\hspace*{-1cm}
\includegraphics[scale=0.09]{figures/pws}
\caption{Sensitivity analysis of Photochemical Water Splitting. Red dots indicate points that are zero values, while blue dots indicate non-zero values.}
\label{pws}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.12]{figures/satechsh2}
\caption{Sensitivity analysis of hydrogen generation technologies \gls{SOEC} and \gls{PEMEC}}.
\label{satechs-h2}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.12]{figures/satechselc}
\caption{Sensitivity analysis of electricity generation technologies \gls{SOFC} and \gls{CCS} gas.}
\label{satechs-elc}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.15]{figures/syscost}
\caption{Sensitivity analysis of the model's overall transition cost between 2013-2100 with respect to selected model parameters.}
\label{syscost}
\end{figure}

\begin{figure}[h] 
\centering
\hspace*{-3cm}
\includegraphics[scale=0.07]{figures/useless}
\caption{Sensitivity analysis results for \gls{PEMFC} and \gls{CCS} coal.}
\label{sa-useless}

\end{figure}

### 2020-11-26 doc/2020-03-paper/acks.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

@@

>>>>

The author(s) gratefully acknowledge the support of the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology. We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.

@@

Anshuman Chaube designed simulation models, conducted sensitivity analysis, and wrote the original draft of the paper.

Andrew Chapman conceived and contributed to conception of the simulations, designed simulation models, and wrote the original draft of the paper.

Akari Minami translated data from Japanese to English, and assisted with testing and performing simulations.

James Stubbins supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.

### 2020-11-26 doc/2020-03-paper/conclusion.tex
added results details
Former-commit-id: ed19f4a90ca89ba623e169f45f26da001cb413db
Former-commit-id: d18cad00c2db357dbb0f67988ccf31fec6140bba
adds clean results for syscost, net emissions
Former-commit-id: 5a0d7dd093d146c65fbf51a7f4887799ed403066
Former-commit-id: 8d484390baa9c26c0788b9cfa933ef94f0c1e0fc
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

\section{Conclusion} \label{Conclusion}
Conclusion
\section{Future work}
FUTURE WORK

\section{Declaration of Competing Interest}

NECESARY?

>>>>

\section{Conclusion} \label{Conclusion}
%what we did. sum up key technologies, what needs to happen for technologies that are not "key", importance of rapid change/suggested timeline.

We simulated five transition scenarios, assessing potential pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply system, and their long-term impact upto 2100. Scenario 1 (Fig. \ref{scen1}), proved that meeting emission goals without new nuclear or new low-emission technologies is infeasible, and such an endeavour is likely to be an expensive failure. The remaining scenarios demonstrate that emission goals can be met by either investing heavily in nuclear (Fig. \ref{scen2}), investing heavily in hydrogen (Fig. \ref{scen3} and \ref{scen5}), or using a combination of both (Fig. \ref{scen4}). Scenarios that incorporate nuclear are the most cost-effective, and using a combination of nuclear and hydrogen leads to the greatest emission reduction post-2050. Key technologies that emerge from our results include nuclear power and hydrogen from renewables, while \gls{CCS} with natural gas and photochemical water splitting (\gls{PWS}) play a nominal role. CCS with coal, steam reforming with our without CCS, new coal, and new oil are not utilized due to their high direct and life-cycle emissions. Our analysis indicates that while politically challenging, a hybrid nuclear-hydrogen strategy is economically feasible and results in long-term emission reduction. Such a multifaceted approach to emission reduction is also likely to improve decarbonization outcomes since the commercialization and deployment of hydrogen in time to meet 2030 and 2050 emission goals is uncertain.

Future work should incorporate synergistic assessment of hydrogen across multiple sectors such as transportation and industry. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonization strategies, improve social outcomes, and delineate investment goals for the energy sector.

%\section{Future work}
%grid resilience - analysis of grid stability of similar mixes at the resolution of minutes. Maybe in TIMES (ugh).
\section{Declaration of Competing Interest}
The authors declare no conflict of interest.

### 2020-11-26 doc/2020-03-paper/discussion.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

%urgency
As the results of all base case scenarios indicate, rapid retirement of fossil fuels and deployment of carbon neutral technologies is urgently required to achieve emission reduction targets in Japan. All coal and oil plants need to be shut down between 2025-2030, and natural gas use must be reduced dramatically. It is also imperative that the existing nuclear reactors be operated at full capacity by 2022. Since hydrogen plays a key role in zero to moderate nuclear deployment scenarios (Figs. \ref{scen3}and \ref{scen4}), it appears prudent to invest in hydrogen power. As the model uses learning curves for technology prices and our objective function is transition cost, hydrogen technologies are deployed as late as possible in order to minimize costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals. Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen deployment by 2030 at the latest, in the absence of new nuclear, or by 2035, with new nuclear.

%nuclear
The scenario with the largest nuclear deployment, Scenario 2, also has the lowest transition cost. When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios. It also reduces the cost of the transition from 3,187,940 MUSD in Scenario 3 to 2,804,753 MUSD in Scenario 4, a difference of 12\% of the system cost. The estimated savings due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines. Further, the large emission reductions achieved with the help of nuclear allow natural gas to continue operating until 2100 while also meeting emission goals. As natural gas is well suited to peaking and load-following, when coupled with flexible fuel cell technologies, it could engender in an extremely stable energy system.

For the transitioning energy system in Japan, under all scenarios investigated, nuclear plays a key role in reducing emissions. A potential strategy for Japan could include the reinvigoration of its nuclear energy sector by restarting existing plants, and if politically feasible, constructing new plants, and investing in advanced reactor research. To minimize the environmental impact from life cycle emissions, it is necessary that all existing and any new reactors be operated for a lifetime of 60 years or more at a high capacity factor. Premature decommissioning due to operational problems or lack of public acceptance need to be avoided. Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, increasing public awareness of nuclear's vital role in  mitigating carbon emission is key to achieving 2030 and 2050 emission targets.

%renewables and flexibility
In all scenarios, solar and wind supply a large portion of the electricity demand. Unless large numbers of nuclear power plants are constructed, Japan will need to invest heavily in offshore wind farms by 2030 (Figs. \ref{scen1},\ref{scen3}-\ref{scen5}). If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (\ref{scen1}). Under a scenario with a relatively large share of renewables, grid flexibility becomes extremely important. such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive. As natural gas is the only extant option for load-following, Japan will face a critical choice - whether to incorporate nuclear as in Scenarios 2 and 4 (Figs. \ref{scen2} and \ref{scen4}), or invest heavily in hydrogen (\ref{scen3} and \ref{scen5} to achieve emission cuts while simultaneously keeping natural gas operational for load-following. Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand. Any fuel cell technology utilized must also be extremely flexible and responsive. Since the model prioritizes \gls{SOFC}s over \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.

%batteries
Lithium-ion is the preferred storage medium in the absence of hydrogen. However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts. While lithium may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium-ion storage if it is relied upon as the primary storage medium. It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals. The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing. If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (\ref{scen3}-\ref{scen5}).

%hydrogen - key players, key parameters, path forward?
After nuclear, hydrogen power emerges as the second most efficacious technology for achieving 2050 emission goals. As seen in the sensitivity analysis results, hydrogen maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector. While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s respectively to recreate similar energy mixes. Key technologies that aid in decarbonization in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation. Steam reforming, with or without CCS, does not get utilized in our simulations due to its high emission coefficient. At the lower end of the technology readiness scale, \gls{SOEC}s emerge as tremendously disruptive due to their high efficiency. However, their operational lifetimes need to be increased significantly, life cycle emissions must be kept low, and cost-competitiveness with \gls{PEMEC}s must be achieved in order to realize their potential. \gls{PWS} plays a marginal role as it is not cost-competitive with electrolysis. From the simulation output data, the investment cost of \gls{SOFC}s emerges as a critical parameter. Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible. However, low response times and high availability are two key factors that are implicit in our assumptions. If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and closer to commercialization. In Scenarios 3 and 4, solar, wind, and nuclear are used to generate hydrogen. Therefore it would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants. Waste heat from nuclear could also be used to produce hydrogen, and would reduce reliance on renewables for electrolysis. As mentioned previously, more flexible and responsive fuel cells and electrolyzers are likely to be the dominant technology in such a system.

%ccs
CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen. Its share is found to be largely insensitive to  investment costs as evidenced by the sensitivity analysis. This is mainly due to its large emission coefficient. Marginal gains are expected in its penetration if the efficiency of CCS is increased to reduce its direct emissions. Reducing indirect emissions is likely to have a greater impact. This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.

>>>>

%urgency
As the results of all base case scenarios indicate, rapid retirement of fossil fuels and deployment of carbon neutral technologies is urgently required to achieve emission reduction targets in Japan. All coal and oil plants need to be shut down between 2025-2030, and natural gas use must be reduced dramatically. It is also imperative that the existing nuclear reactors be operated at full capacity by 2022. Since hydrogen plays a key role in zero to moderate nuclear deployment scenarios (Figs. \ref{scen3} and \ref{scen4}), it appears prudent to invest in hydrogen power. As the model uses learning curves for technology prices and our objective function is transition cost, hydrogen technologies are deployed as late as possible in order to minimize costs by utilizing technologies at their cheapest, while there is still time to deploy them and achieve emission goals. Therefore,  results indicate that it is imperative that Japan deploy an increasing amount of renewables including wind power between 2020-2030, and be prepared to deploy and rapidly scale up hydrogen power by 2030 at the latest in the absence of new nuclear, or by 2035 with new nuclear.

%nuclear
The scenario with the largest nuclear deployment, Scenario 2, also has the lowest transition cost. When used with hydrogen, 50 MW of new nuclear results in the greatest reduction in emissions after 2050 out of all 5 scenarios. It also reduces the cost of the transition from 3.18 Trillion USD in Scenario 3 to 2.80 Trillion USD in Scenario 4, a difference of 12\% of the system cost. The estimated savings in cost and emissions due to nuclear are conservative, as we have not incorporated the cost of transporting hydrogen utilizing tankers or pipelines. The large emission cuts achieved with the help of nuclear also allow natural gas to continue operating until 2100, while meeting emission goals. As natural gas is well suited to peaking and load-following, when coupled with flexible fuel cell technologies, it could engender in an extremely stable energy system.

For the transitioning energy system in Japan, under all scenarios investigated, nuclear plays a key role in reducing emissions. A potential strategy for Japan could include the reinvigoration of its nuclear energy sector by restarting existing plants, and if politically feasible, constructing new plants, and investing in advanced reactor research. To minimize the environmental impact from life cycle emissions, it is necessary that all existing and any new reactors be operated for a lifetime of 60 years or more at a high capacity factor. Premature decommissioning due to operational problems or lack of public acceptance need to be avoided. Therefore, prioritizing reactor safety for resilience to disasters and in order to regain the public's trust in nuclear power, and increasing public awareness of nuclear's vital role in mitigating carbon emission is key to achieving 2030 and 2050 emission targets.

%renewables and flexibility
In all scenarios, solar and wind supply a large portion of the electricity demand. Unless large numbers of nuclear power plants are constructed, Japan will need to invest heavily in offshore wind farms by 2030 (Figs. \ref{scen1},\ref{scen3}-\ref{scen5}). If hydrogen and CCS are not deployed by 2035, investment in offshore floating turbines may also become necessary (Fig. \ref{scen1}). Under a scenario with a relatively large share of renewables, grid flexibility becomes extremely important. Such a scenario requires significant investment in storage technologies, and ensuring that all emerging technologies are flexible and responsive. As natural gas is the only extant option for load-following, it is necessary to invest in nuclear or hydrogen to achieve emission cuts while simultaneously keeping natural gas operational for load-following. Additionally, any nuclear power plants and fossil fuel power plants which use CCS must be able to load-follow, or be coupled to storage, ideally electrolysers, in order to store excess electricity for peak demand. Any fuel cell technology utilized must also be extremely flexible and responsive. Since the model prioritizes \gls{SOFC}s over \gls{PEMFC}s due to their higher efficiency, it is important that \gls{SOFC}s reduce their startup times to have an edge over \gls{PEMFC}s in utility-scale applications.

%batteries
Lithium-ion is the preferred storage medium in the absence of hydrogen. However, as the base case scenarios indicate, extremely large capacities of storage must be deployed to achieve a stable grid that can sustain the large capacities of renewables required for deep emission cuts. While lithium may be available, cobalt and manganese reserves are limited \cite{scrosati_lithium-ion_2011,simon_potential_2015,turcheniuk_ten_2018} , which may inflate the prices of lithium-ion storage if it is relied upon as the primary storage medium. It may be preferable to redesign batteries to reduce the amount of rare minerals used in their manufacturing, and improve recycling to increase the recovery rate of rare metals. The life cycle emissions from batteries must also be reduced by using cleaner materials and electricity for manufacturing. If hydrogen storage is available, battery storage storage serves as a near-term transition technology after which hydrogen storage dominates (Figs. \ref{scen3}-\ref{scen5}).

%hydrogen - key players, key parameters, path forward?
After nuclear, hydrogen power emerges as the second most efficacious technology for achieving 2050 emission goals. As seen in the sensitivity analysis results, hydrogen maintains a significant share of the electricity mix despite a wide range of perturbations to key parameters of the hydrogen sector. While \gls{SOFC}s and \gls{SOEC}s are preferred over \gls{PEMFC}s and \gls{PEMEC}s in all of our simulations, the role of hydrogen is so important that if \gls{SOFC} or \gls{SOEC} deployment is disabled, the model replaces them with inferior \gls{PEMFC}s or \gls{PEMEC}s respectively to recreate similar energy mixes. Key technologies that aid in decarbonization in our simulations are \gls{SOFC}s and \gls{PEMEC}s, which are close to maturation. Steam reforming, with or without CCS, does not get utilized in our simulations due to its high emission coefficient. At the lower end of the technology readiness scale, \gls{SOEC}s emerge as tremendously disruptive due to their high efficiency. However, their operational lifetimes need to be increased significantly, life cycle emissions must be kept low, and cost-competitiveness with \gls{PEMEC}s must be achieved in order to realize their potential. \gls{PWS} plays a marginal role as it is not cost-competitive with electrolysis. From the simulation output data, the investment cost of \gls{SOFC}s emerges as a critical parameter. Therefore it is vital to reduce fuel cell investment costs to make deep emission reduction economically feasible. However, low response times and high availability are two other key factors that are implicit in our assumptions. If \gls{SOFC}s are not as flexible as assumed, they are replaced in our simulations by \gls{PEMFC}s, which are known to be more flexible and closer to commercialization. In Scenarios 3 and 4, solar, wind, and nuclear are used to generate hydrogen. Therefore it would be economically favourable to couple utility-scale renewables and nuclear power plants with electrolysis plants. Waste heat from nuclear could also be used to produce hydrogen, and would reduce reliance on renewables for electrolysis. As mentioned previously, more flexible and responsive fuel cells and electrolyzers are likely to be the dominant technology in such a system.

%ccs
CCS plays a small role in our base case scenarios as a transitional technology, despite being cheaper than hydrogen. Its share is found to be largely insensitive to its investment costs as evidenced by the sensitivity analysis. This is mainly due to its large emission coefficient. Marginal gains are expected in its penetration if the efficiency of CCS is increased to reduce its direct emissions. Reducing indirect emissions is likely to have a greater impact. This could be achieved in the future by increased electrification of the industrial sector, and the use of hydrogen to produce steel.

Although our analysis relies on optimal solutions and scenarios and is technologically agnostic, policy makers in Japan will face difficult future decisions as to the long-term nature of the low-carbon energy system. One approach could be to prioritize nuclear energy and to reap the benefits of inexpensive, low-carbon energy, at the cost of achieving consensus from the public for its long-term deployment and use. Another low carbon energy pathway proposed by our results is a transition toward a hydrogen economy, utilizing hydrogen as a storage medium to engender significant deployment of renewable energy. The hydrogen pathway also provides more energy security, obviating the use of coal and oil and mitigating the use of natural gas. As social opposition to nuclear is a prominent issue in Japan, the deployment of a parallel nuclear and hydrogen-based energy system is unlikely. However, our results indicate that these two approaches are not mutually exclusive. The cost of transitioning to a hydrogen energy system without deploying any new nuclear is much higher than that of any of the nuclear-inclusive options. Deploying nuclear in tandem with hydrogen provides a cost-effective compromise. An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as at the time of writing, the timely success of the Japanese hydrogen plan is far from certain. At the very least, as is the case for CCS and fossil fuels, nuclear power may offer a "bridging" option, providing a low-carbon pathway in the short term through extended nuclear lifetimes and limited new builds, allowing sufficient time for the maturation of hydrogen and renewable-based energy options for longer-term deployment timelines. If supported politically, long-term use of nuclear power could provide emission cuts well beyond the 2050 targets. Policy which is cognizant of these economic, environmental, and social aspects of energy systems is required to deliver a low-cost, low-carbon energy future for Japan which is socially acceptable.

### 2020-11-26 doc/2020-03-paper/introduction.tex
updated manuscript
Former-commit-id: 0d294a359d06924d4184e24341dc22f2d6042ab9
Former-commit-id: 65a1df1c9126e751309ade12977d50d3ec04feaa

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies (ANRE, 2018). The Plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid). Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met. This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies \cite{ashina_roadmap_2012}. It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan. The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.

>>>>

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition and approved by the Cabinet in July of 2018 \cite{noauthor_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident and external pressures on energy supplies \cite{noauthor_annual_2018}. The Plan reaffirms the Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and a consideration of the environment (summarized as '3E+S'; ibid). Although there are some parallels between the 3E+S goals and the Paris Agreement targets agreed to by Japan, the plan does not set out in detail how the 2050 emission reduction target of 80\% is to be met. This may be due to the lack of evidence for the economically feasible reduction of GHG emissions in each sector, and it has been suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by electricity generated from low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilizing existing technologies is preferable to delaying action in preference for future technologies \cite{ashina_roadmap_2012}. It is likely that a mixture of current and emerging technologies will be employed to achieve carbon reduction targets in Japan. The strategies currently under consideration include a reinvigoration of the nuclear contribution to final energy demand, deploying \gls{CCS} to fossil fuel power plants, and the ushering in of the hydrogen economy, underpinned by renewable energy deployment as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, noauthor_basic_2017}.
